\documentclass[a4paper,11pt]{article}
\usepackage{fullpage}
\usepackage[colorlinks=true]{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{lmodern}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{color}
%\usepackage{bibtex}

\setlength{\headheight}{30pt}
\setlength{\headsep}{0.2in}

\definecolor{gray}{rgb}{0.5, 0.5, 0.5}

\lstset{
    language=Python,
    basicstyle=\footnotesize,
    numbers=left,
    numberstyle=\scriptsize\color{gray},
    stepnumber=1,
    numbersep=5pt,
    backgroundcolor=\color{white},
    showspaces=false,
    showstringspaces=false,
    rulecolor=\black,
    tabsize=4,
    captionpos=t,
    breaklines=true,
    keywordstyle=\color{black},
    commentstyle=\color{black},
    stringstyle=\color{black}
}

\title{OpenCUDA+MPI\\
       A Framework for Heterogeneous GP-GPU Distribute Computing}
\date{\today}
\author{Kenny Ballou\\
        College of Engineering -- Department of Computer Science\\
        Boise State University\\
        Alark Joshi, Ph. D}

\lhead{\fancyplain{}{Student Research Initiative 2013\\
                     Progress Report}}
\pagestyle{empty}

\begin{document}
\input{./title.tex}
\nocite{*}
\thispagestyle{fancy}
\abstract{The introduction and rise of General Purpose Graphics Computing has
significantly impacted parallel and high-performance computing. Even worse, it
has brought about even more challenges when it comes to distributed computing
(with GPU's). Current solutions target specifics: specific hardware, specific
network topology, a specific level of sameness. What if we could ignore
specifics? What if we could write a general algorithm to solve a problem and
have a job scheduler do the rest? That is the goal of OpenCUDA+MPI. To achieve
this goal, we have written a framework that allows a developer/ data scientist
to write a general algorithm/ solution without the overhead of worrying about
the specifics of the cluster it will run against. We have found, [nothing yet]
and, therefore, can conclude [also nothing].}\\

\textbf{Keywords:} Parallel Computing, Distributed Computing, General Purpose
Graphics Processing, High-Performance Computing, Scientific Computing
\include{Introduction}
\include{Methodology}
%\include{Results}
%\include{Discussion}
%\include{Conclusions}
\appendix
%\include{Appendices}
\include{Reference}
\end{document}
