% vim: syntax=tex:
\section{Significance}
\texttt{CUDA+MPI} will serve to better utilization of existing computing
resources. In other words, it will grant us high compute power at low 
combutational cost.

%---added the section below ---%
Many existing schedulers and/or frameworks serving this goal work well with 
homogeneous hardware systems. Cluster that hold different architectures or have 
different \gls{cuda}-enabled cards are not able to utilize existing frameworks 
to take full advantage of processing power available. 
There is a substantial need for ...

%--- a lot of things below need to be re-worded ----%
Many personal computers have a \gls{cuda} graphics card. It 
is more cost effective to build a cluster of multiple computers than to purchase
a supercomputer toperform high performance computing. The reason for the low 
costs stem from the fact that clusters are built of components which are sold 
in high volumes \cite{erdt2008automatic}. \texttt{CUDA+MPI} will have the 
advantage of handling heterogeneous distributed computing. In other words, 
\texttt{CUDA+MPI} avoids hardware limitations. All the computers participating 
in the cluster do not need to have the same model of \gls{cuda}-enabled 
\gls{gpu} cards. This will also give us the freedom to easily add new nodes to 
the cluster as needed.

Since \texttt{CUDA+MPI} will operate in a heterogeneous cluster it will manage
the job requests from the user to be run on a heterogeneous cluster of
\gls{gpu}-capable computers. In order to decide job priority, amount of work
and availability of devices will be considered. In addition to improved
performance, the proposed framework will grant researchers and scientists the
assurance that the heterogeneous cluster will be optimized for computing
without requiring extra effort and thought.
